Statistical Inference: Peer Assessment 2
==========================================
Created by Simon Mackinnon on `r format(Sys.Date(), "%B %d, %Y")`
[Statistical Inference - Coursera](https://www.coursera.org/course/statinference)

## Assignment 1

### Overview
In a few (2-3) sentences explain what is going to be reported on.

### Settings
```{r settings}
library(datasets)
library(ggplot2)
library(gridExtra)
```

### Data Processing

```{r dataReading, echo=TRUE}
# copy to global environment
ToothGrowthDataFrame <- ToothGrowth

#confirm the number dimensions of the copied data
dim(ToothGrowthDataFrame)

#and display the head rows
head(ToothGrowthDataFrame)
```

There are **`r nrow(ToothGrowthDataFrame)` rows** and **`r ncol(ToothGrowthDataFrame)` columns** in the copied data.


### Simulations

#### Sample Mean versus Theoretical Mean

```{r Sample Mean versus Theoretical Mean, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}
lambda <- 0.2
n = 1000

hist(rexp(n, lambda))

mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(40)))
hist(mns)

```

#### Sample Variance versus Theoretical Variance

```{r Sample Variance versus Theoretical Variance, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}
lambda <- 0.2
n = 1000

hist(rexp(n, lambda))

mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(40)))
hist(mns)

```

#### Distribution

```{r Distribution, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}

#plots
p1 <- qplot(ToothGrowthDataFrame$len, 
            ToothGrowthDataFrame$supp, 
            colour=I("blue")) +
            xlab("Len") + 
            ylab("Supp") + 
            ggtitle("Len vs Supp")

p2 <- qplot(ToothGrowthDataFrame$len, 
            ToothGrowthDataFrame$dose, 
            colour=I("blue")) +
            xlab("Len") + 
            ylab("Dose") + 
            ggtitle("Len vs Dose")

p3 <- qplot(ToothGrowthDataFrame$supp, 
            ToothGrowthDataFrame$dose, 
            colour=I("blue")) +
            xlab("Supp") + 
            ylab("Dose") + 
            ggtitle("Supp vs Dose")

grid.arrange(p1, p2, p3, ncol = 3, main = "ToothGrowth")

```


