Statistical Inference: Peer Assessment 2
==========================================
Created by Simon Mackinnon on `r format(Sys.Date(), "%B %d, %Y")`
[Statistical Inference - Coursera](https://www.coursera.org/course/statinference)

## Assignment 1

### Overview
In a few (2-3) sentences explain what is going to be reported on.

 The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda

### Settings
```{r settings}
library(datasets)
library(ggplot2)
library(gridExtra)
```

### Simulations

#### Sample Mean versus Theoretical Mean

```{r Sample Mean versus Theoretical Mean, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}
lambda <- 0.2
n = 40
no_sims <- 1000

theoretical_mean = 1/lambda

sample_data_means = apply(matrix(rexp(no_sims*n, rate = lambda), no_sims), 1, mean)
hist(sample_data_means)

abline(v = theoretical_mean, col = "red")


theoretical_mean

sample_mean <- mean(sample_data_means)
sample_mean

```

#### Sample Variance versus Theoretical Variance

```{r Sample Variance versus Theoretical Variance, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}

theoretical_standard_deviation <- 1/lambda

#Note: Variance = (SD)^2 / n
theoretical_variance <- (theoretical_standard_deviation^2) / n

sample_variance <- var(sample_data_means)

theoretical_variance
sample_variance

```

#### Normal Distribution Approximation

```{r Normal Distribution Approximation, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}

hist(rexp(no_sims))
mns = NULL
for (i in 1 : 1000) mns = c(mns, mean(rexp(n)))
hist(mns)

```


#### Distribution

```{r Distribution, echo=TRUE, fig.align='center', fig.width=10, fig.height=5}

summary(ToothGrowth)

#plots
p1 <- qplot(ToothGrowth$len, 
            ToothGrowth$supp, 
            colour=I("blue")) +
            xlab("Len") + 
            ylab("Supp") + 
            ggtitle("Len vs Supp")

p2 <- qplot(ToothGrowth$len, 
            ToothGrowth$dose, 
            colour=I("blue")) +
            xlab("Len") + 
            ylab("Dose") + 
            ggtitle("Len vs Dose")

p3 <- qplot(ToothGrowth$supp, 
            ToothGrowth$dose, 
            colour=I("blue")) +
            xlab("Supp") + 
            ylab("Dose") + 
            ggtitle("Supp vs Dose")

grid.arrange(p1, p2, p3, ncol = 3, main = "ToothGrowth")

```


